---
title: "Lec 11 Participation converted to RMD"
output:
  html_document: default
  pdf_document: default
---

```{r allow errors, warning=FALSE}
library("tidyverse")
library("gapminder")
```


```{r}
gapminder
write_csv(gapminder,'./gapminder.csv')
view(gapminder)
```

Calculate mean life Exp per continent

```{r}
gapminder_sum <- gapminder %>% 
   group_by(continent) %>% 
  summarize(ave_lifeExp=mean(lifeExp))
```



```{r}
gapminder_sum %>% 
  ggplot
```


Part II
```{r warning=FALSE}
gapminder_csv <- read_csv('./gampinder_sum.csv') #on windows, it is .\gapminder_sum.csv

```

another way of using here #is platform agnostic, dir-structure agnostic

```{r}
read_csv(here::here("test","tes","te","t",gapminder_sum.csv))

```

couple more things about here
set_here()

```{r}
view(gapminder_csv)
```

in here:
```{r}
write_csv(gapminder_sum, here::here("gapminder_sum.csv"))
ls()
list=ls()
remove(list=ls())
```


ls() #only removes the variables, the packages are still not detached

```{r}
library("tidyverse")
library("here")
```



read Excel file

Datafiles from this tutorial: https://beanumber.github.io/sds192


```{r}
data_url <- "http://gattonweb.uky.edu/sheather/book/docs/datasets/GreatestGivers.xls"
```

# read_csv can directly import URLs but read_excel requires you to download it first.


```{r}
read_csv(url)
download.file(url=data_url, destfile = paste('./datasets/',file_name))
```

CLS files may not work on windows
 Task: change above to use the "here::here" package:


```{r}
download.file(url=data_url, destfile = here::here("test","greatestGiver.xls"))
```

```{r}
install.packages("readxl")
library(readxl)
philanthropists <-read_excel(here::here)
```


```{r}
xls_url <- "http://gattonweb.uky.edu/sheather/book/docs/datasets/GreatestGivers.xls"
download.file(xls_url,here::here("data","cm011_data","some_file.xls"))
```


```{r}
file_name <- basename(xls_url)
download.file(xls_url,here::here("data","cm011_data",file_name))
```



```{r}
read_excel(here::here("data","cm011_data",file_name))
```


```{r}
mri_file = here::here("data","cm011_data","Firas-MRI.xlsx")
mri <- read_excel(mri_file, range = "A1:K12")
```


```{r}
mri_file = here::here("data","cm011_data","Firas-MRI.xlsx")
mri <- read_excel(mri_file, range = "A1:L12")
```


```{r}
mri <- mri %>% 
  tidyr::pivot_longer(cols = `Slice 1`:`Slice 8`,
    names_to = 'slice_no',
    values_to = 'value')
mri
```

assign the imported data to excel file:


```{r}
view(philanthropists)
```

```{r}
head(philanthropists)
```






